Code Clones: To refactor or not to refactor?

### 2020-05-09 ase/paper.tex
Updates from Overleaf

However, several studies show that not all clones should be refactored~\cite{jarzabek2010clones, kapser2008cloning}. This can be due to variance between cloned fragments~\cite{roy2007survey} or parts of the codebase that have a low coupling and evolve separately~\cite{jarzabek2010clones}. There are many tools to detect clones \cite{roy2007survey, sheneamer2016survey, svajlenko2014evaluating, gautam2016various} that can find similar pieces of code, but none show to which extent these are relevant refactoring candidates.

@@

Most clone detection tools can be configured using thresholds. These thresholds indicate the minimum number of lines, tokens and/or statements that must be spanned for duplicate fragments to be considered clones. Often, such thresholds are intuitively chosen~\cite{li2006cp, roy2009mutation} or based on a quantile distribution of empirical data~\cite{alves2010deriving}. Using the delta maintainability score we can find support for which thresholds should be chosen to increase the chance to find clones that improve maintainability when refactored.

Over a corpus of 2,267 Java project our tool refactored 12,710 clone classes. We find that the main influencing factor on maintainability when refactored is clone volume. %We define token volume as the combined number of tokens in all clone instances in a clone class. %When refactoring clones with a very small token volume, we found that the maintainability decreases when such clones are refactored. 
The average clone with a volume of 63 or more tokens improves maintainability when refactored. The other factor with a major influence on maintainability is the number of parameters that are required for the extracted method. We find that if a clone requires more than 2 parameters in the extracted method, it is more likely to decrease maintainability.

@@

We also limited our scope by choosing a set of four metrics. However, software maintainability depends on more factors and can be measured by more metrics. By taking more metrics into account, we can give a better indication whether the maintainability improves after refactoring. For instance, we think that module coupling \cite{heitlager2007practical} is an important metric to be considered when refactoring clones. In out future work we will investigate other metrics and map their impact on the results.

>>>>

However, several studies show that not all clones should be refactored~\cite{jarzabek2010clones, kapser2008cloning}. This can be due to semantical variance between cloned fragments~\cite{roy2007survey} or parts of the codebase that have a low coupling and evolve separately~\cite{jarzabek2010clones}. There are many tools to detect clones \cite{roy2007survey, sheneamer2016survey, svajlenko2014evaluating, gautam2016various} that can find similar pieces of code, but none show to which extent these are relevant refactoring candidates.

@@

Most clone detection tools can be configured using thresholds. These thresholds indicate the minimum number of lines, tokens and/or statements that must be spanned for duplicate fragments to be considered clones. Often, such thresholds are intuitively chosen~\cite{li2006cp, roy2009mutation} or based on a quantile distribution of empirical data~\cite{alves2010deriving}. Using the delta score we can find support for which thresholds should be chosen to increase the chance to find clones that improve maintainability when refactored.

Over a corpus of 2,267 Java project our tool refactors 12,710 clone classes. We find that the main influencing factor on maintainability when refactored is clone volume. %We define token volume as the combined number of tokens in all clone instances in a clone class. %When refactoring clones with a very small token volume, we found that the maintainability decreases when such clones are refactored. 
The average clone with a volume of 63 or more tokens improves maintainability when refactored. The other factor with a major influence on maintainability is the number of parameters that are required for the extracted method. We find that if a clone requires more than 2 parameters in the extracted method, it is more likely to decrease maintainability.

@@

We also limited our scope by choosing a set of four metrics. However, software maintainability depends on more factors and can be measured by more metrics. By taking more metrics into account, we can give a better indication whether the maintainability improves after refactoring. For instance, we think that module coupling \cite{heitlager2007practical} is an important metric to be considered when refactoring clones. In future work we will investigate other groups of maintainability metrics to broaden the understanding of factors influencing the desirability of a refactoring.
